Fast Hyperparameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning

### 2017-02-04 paper.tex
norma
aggiornamento figure
inserito algoritmo

% My commands
\newcommand{\Real}{\mathbb{R}}
\newcommand{\Natu}{\mathbb{N}}
\newcommand{\dd}{{\bf d}}
\newcommand{\xx}{{\bf x}}
\newcommand{\yy}{{\bf y}}
\newcommand{\zz}{{\bf z}}
\newcommand{\ff}{{\bf f}}
\newcommand{\ww}{{\bf w}}
\newcommand{\vv}{{\bf v}}
\newcommand{\AAA}{{\bf A}}
\newcommand{\CC}{{\bf C}}
\newcommand{\DD}{{\bf D}}
\newcommand{\EE}{{\bf E}}
\newcommand{\GG}{{\bf G}}
\newcommand{\KK}{{\bf K}}
\newcommand{\YY}{{\bf Y}}
\newcommand{\MM}{{\bf M}}
\newcommand{\HH}{{\bf H}}
\newcommand{\II}{{\bf I}}
\newcommand{\XX}{{\bf X}}
%\newcommand{\NN}{{\bf N}}
\newcommand{\cU}{{\cal U}}
\newcommand{\cI}{{\cal I}}
\newcommand{\cR}{{\cal R}}
\newcommand{\cN}{{\cal N}}
\newcommand{\cQ}{{\mathcal Q}}
\newcommand{\1}{{\bf 1}}
\newcommand{\Exp}{\mathbb{E}}
\newcommand{\labelfun}{L}
\newcommand{\node}{v}
\newcommand{\cK}{{\cal K}}
%\newtheorem{lemma}{Lemma}
%\newtheorem{theorem}{Theorem}
%\newtheorem{corollary}{Corollary}
%\newtheorem{proposition}{Proposition}
%\newtheorem{definition}{Definition}
%\newtheorem{remark}{Remark}
\newcommand{\cC}{{\cal C}}
\newcommand{\R}{{\mathbb R}}
\newcommand{\N}{{\mathbb N}}
\newcommand{\ggamma}{\pmb{\gamma}}
\newcommand{\aalpha}{\pmb{\alpha}}
\newcommand{\bbeta}{\pmb{\beta}}
\newcommand{\eeta}{\pmb{\eta}}
\newcommand{\ssigma}{\pmb{\sigma}}
\newcommand{\llambda}{\pmb{\lambda}}
\newcommand{\mmu}{\pmb{\mu}}
\newcommand{\pphi}{\pmb{\phi}}

@@

\subsubsection{EasyMKL}
\label{EasyMKL}
EasyMKL \cite{Aiolli2015} is a recent MKL algorithm able to combine sets of basic kernels by solving a simple quadratic optimization problem. Besides its proved empirical effectiveness, a clear advantage of EasyMKL compared to other MKL methods is its high scalability with respect to the number of kernels to be combined. Specifically, its computational complexity is constant in memory and linear in time.
EasyMKL finds the coefficients $\boldsymbol{\eta}$ that maximize the margin on the training set, where the margin is computed as the distance between the convex hulls of positive and negative examples. In particular, the general problem EasyMKL tries to optimize is the following:
\vspace{-0.4cm}
\begin{equation}
\label{eq:easymklotig}
\max_{\boldsymbol{\eta}:||\boldsymbol{\eta}||_2=1} \min_{\boldsymbol{\gamma} \in \Gamma} \mbox { }  \boldsymbol{\gamma}^{\top} \YY ( \sum_{r=0}^R \eta_r \KK_r) \YY \boldsymbol{\gamma} + \Lambda ||\boldsymbol{\gamma}||^2,
\end{equation}
%\vspace{-0.1cm}
where $\YY$ is a diagonal matrix with training labels on the diagonal, and $\Lambda$ is a regularization hyperparameter. The domain $\Gamma$ represents two probability distributions over the set of positive and negative examples of the training set, that is $\Gamma = \{\boldsymbol{\gamma} \in \Real_+^{\ell} \hspace{0.2cm} |  \sum_{y_i = +1} \boldsymbol{\gamma}_i = 1 , \sum_{y_i = -1} \boldsymbol{\gamma}_i = 1\}.
$
Note that any element $\boldsymbol{\gamma} \in \Gamma$ corresponds to a pair of points, the first in the convex hull of positive training examples and the second in the convex hull of negative training examples.
At the solution, the first term of the objective function represents the obtained margin, that is the (squared) distance between a point in the convex hull of positive examples and a point in the convex hull of negative examples, in the compounded feature space.
%The objective function in Eq. \ref{eq:easymklotig} can be interpreted as the dual problem of a regularized empirical objective function using the kernel $\sum_{r=1}^R \eta_r \KK_r$.
Eq. \ref{eq:easymklotig} is a minimax problem that can be reduced  to a simple quadratic problem with a technical derivation described  in \cite{Aiolli2015}. %The solution of the quadratic problem is an optimal $\ggamma^*$ for the original min-max formulation. Due to the particular structure of EasyMKL, it is sufficient to provide the average kernel of all the basic kernels ($\KK^A = \frac{1}{R} \sum_{r=1}^R \frac{\KK_r}{Tr(\KK_r)}$). From $\ggamma^*$, it is easy to obtain the optimal weights for the single basic kernels $\KK_r$ by using the following formula
%\begin{equation}
%\label{eq:easyeta}
%	\eta_r = \gamma^{*T} \YY \,\, (\KK_r/Tr(\KK_r)) \,\, \YY \gamma^*, \,\,\,\, \forall r=1,\dots,R.
%\end{equation}
In the following sections, we will refer to this method as EasyMKL\footnote{EasyMKL implementation: github.com/jmikko/EasyMKL}.
%and we have to provide it only $\KK^A$, the dataset $\XX$ and $\yy$ to evaluate equation \ref{eq:easyeta}, and the EasyMKL regularization hyperparameter $\Lambda$.

@@

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.42\textwidth]{img/CPDB_jaccard.png}
\includegraphics[width=0.42\textwidth]{img/GDD_jaccard.png}
\caption{Average jaccard values and standard deviation in 50 runs between the indices of top kernels using a subset of training data and using the whole set.}
\label{fig:jaccard}
\end{figure}

>>>>

\usepackage{color}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\usepackage{listings}
\lstset{
	language=Python,
	basicstyle=\footnotesize,
	commentstyle=\color{mygreen},
	frame=single,
	keepspaces=true,
	keywordstyle=\color{blue},
	morekeywords={*,...},
	escapeinside={(*}{*)}, 
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray}, 
	rulecolor=\color{black},
	title=Proposed algorithm	
}

% My commands
\newcommand{\Real}{\mathbb{R}}
\newcommand{\Natu}{\mathbb{N}}
\newcommand{\dd}{{\bf d}}
\newcommand{\xx}{{\bf x}}
\newcommand{\yy}{{\bf y}}
\newcommand{\zz}{{\bf z}}
\newcommand{\ff}{{\bf f}}
\newcommand{\ww}{{\bf w}}
\newcommand{\vv}{{\bf v}}
\newcommand{\AAA}{{\bf A}}
\newcommand{\CC}{{\bf C}}
\newcommand{\DD}{{\bf D}}
\newcommand{\EE}{{\bf E}}
\newcommand{\GG}{{\bf G}}
\newcommand{\KK}{{\bf K}}
\newcommand{\YY}{{\bf Y}}
\newcommand{\MM}{{\bf M}}
\newcommand{\HH}{{\bf H}}
\newcommand{\II}{{\bf I}}
\newcommand{\XX}{{\bf X}}
\newcommand{\XXs}{{\XX_\textsc{s}}}
%\newcommand{\NN}{{\bf N}}
\newcommand{\cU}{{\cal U}}
\newcommand{\cI}{{\cal I}}
\newcommand{\cR}{{\cal R}}
\newcommand{\cN}{{\cal N}}
\newcommand{\cQ}{{\mathcal Q}}
\newcommand{\1}{{\bf 1}}
\newcommand{\Exp}{\mathbb{E}}
\newcommand{\labelfun}{L}
\newcommand{\node}{v}
\newcommand{\cK}{{\cal K}}
%\newtheorem{lemma}{Lemma}
%\newtheorem{theorem}{Theorem}
%\newtheorem{corollary}{Corollary}
%\newtheorem{proposition}{Proposition}
%\newtheorem{definition}{Definition}
%\newtheorem{remark}{Remark}
\newcommand{\cC}{{\cal C}}
\newcommand{\R}{{\mathbb R}}
\newcommand{\N}{{\mathbb N}}
\newcommand{\ggamma}{\pmb{\gamma}}
\newcommand{\aalpha}{\pmb{\alpha}}
\newcommand{\bbeta}{\pmb{\beta}}
\newcommand{\eeta}{\pmb{\eta}}
\newcommand{\ssigma}{\pmb{\sigma}}
\newcommand{\llambda}{\pmb{\lambda}}
\newcommand{\mmu}{\pmb{\mu}}
\newcommand{\pphi}{\pmb{\phi}}

@@

\subsubsection{EasyMKL}
\label{EasyMKL}
EasyMKL \cite{Aiolli2015} is a recent MKL algorithm able to combine sets of basic kernels by solving a simple quadratic optimization problem. Besides its proved empirical effectiveness, a clear advantage of EasyMKL compared to other MKL methods is its high scalability with respect to the number of kernels to be combined. Specifically, its computational complexity is constant in memory and linear in time.
EasyMKL finds the coefficients $\boldsymbol{\eta}$ that maximize the margin on the training set, where the margin is computed as the distance between the convex hulls of positive and negative examples. In particular, the general problem EasyMKL tries to optimize is the following:
\vspace{-0.4cm}
\begin{equation}
\label{eq:easymklotig}
\max_{\boldsymbol{\eta}:||\boldsymbol{\eta}||_2=1} \min_{\boldsymbol{\gamma} \in \Gamma} \mbox { }  \boldsymbol{\gamma}^{\top} \YY \left( \sum_{r=0}^R \eta_r \KK_r\right) \YY \boldsymbol{\gamma} + \Lambda ||\boldsymbol{\gamma}||^2_2,
\end{equation}
%\vspace{-0.1cm}
where $\YY$ is a diagonal matrix with training labels on the diagonal, and $\Lambda$ is a regularization hyperparameter. The domain $\Gamma$ represents two probability distributions over the set of positive and negative examples of the training set, that is $\Gamma = \{\boldsymbol{\gamma} \in \Real_+^{\ell} \hspace{0.2cm} |  \sum_{y_i = +1} \boldsymbol{\gamma}_i = 1 , \sum_{y_i = -1} \boldsymbol{\gamma}_i = 1\}.
$
Note that any element $\boldsymbol{\gamma} \in \Gamma$ corresponds to a pair of points, the first in the convex hull of positive training examples and the second in the convex hull of negative training examples.
At the solution, the first term of the objective function represents the obtained margin, that is the (squared) distance between a point in the convex hull of positive examples and a point in the convex hull of negative examples, in the compounded feature space.
%The objective function in Eq. \ref{eq:easymklotig} can be interpreted as the dual problem of a regularized empirical objective function using the kernel $\sum_{r=1}^R \eta_r \KK_r$.
Eq. \ref{eq:easymklotig} is a minimax problem that can be reduced  to a simple quadratic problem with a technical derivation described  in \cite{Aiolli2015}. %The solution of the quadratic problem is an optimal $\ggamma^*$ for the original min-max formulation. Due to the particular structure of EasyMKL, it is sufficient to provide the average kernel of all the basic kernels ($\KK^A = \frac{1}{R} \sum_{r=1}^R \frac{\KK_r}{Tr(\KK_r)}$). From $\ggamma^*$, it is easy to obtain the optimal weights for the single basic kernels $\KK_r$ by using the following formula
%\begin{equation}
%\label{eq:easyeta}
%	\eta_r = \gamma^{*T} \YY \,\, (\KK_r/Tr(\KK_r)) \,\, \YY \gamma^*, \,\,\,\, \forall r=1,\dots,R.
%\end{equation}
In the following sections, we will refer to this method as EasyMKL\footnote{EasyMKL implementation: github.com/jmikko/EasyMKL}.
%and we have to provide it only $\KK^A$, the dataset $\XX$ and $\yy$ to evaluate equation \ref{eq:easyeta}, and the EasyMKL regularization hyperparameter $\Lambda$.

@@

\begin{lstlisting}
Input: training matrix (*$\XX$*), list of kernel functions (*$L$*)
(*$\XXs$*) (*$\leftarrow$*) subset_of((*$\XX$*))
(*$KL_\textsc{s}$*) (*$\leftarrow$*) [ker_fun((*$\XXs$*)) for ker_fun in (*$L$*)] #calculate matrices on (*$\XXs$*)
(*$\boldsymbol{\eta}$*) (*$\leftarrow$*) EasyMKL((*$KL_\textsc{s}$*)) #calculate weights
(*$L_{\textsc{top}}$*) (*$\leftarrow$*) top_of((*$L,\boldsymbol{\eta}$*)) #get the top functions
(*$KL$*) (*$\leftarrow$*) [ker_fun((*$\XX$*)) for ker_fun in (*$L_{\textsc{top}}$*)] #calculate top matrices on (*$\XX$*)
\end{lstlisting}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.42\textwidth]{img/CPDBh.png}
\includegraphics[width=0.42\textwidth]{img/GDDh.png}
\caption{Average jaccard values and standard deviation in 50 runs between the indices of top kernels using a subset of training data and using the whole set.}
\label{fig:jaccard}
\end{figure}
